220410_Competition

### 2023-08-14 code/analysis.Rmd
adding covariates and streamlining analysis

## Figure 4 - Split by profitability
```{r}

@@

## Read in Centroid Data
zip.centroids <- read.csv("ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

@@

## Change in Full Market Benefit
```{r}

>>>>

## Figure 4 - Split by profitability

@@

## Read in Centroid Data
zip.centroids <- read.csv("//Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

@@

## Change in Full Market Benefit - CAreful this is not great
```{r}
